Visualizing example of predicted TAD boundaries

### 2020-05-06 Scripts_for_results/02_creating_lineplot_of_balanced_accuracies.Rmd
edits to results scripts
edits

@@

@@

>>>>

```{r}
all_rfperfs <- rbind.data.frame(badata_gm12878_10kb)
all_rfperfs$CL <- rep("GM12878", length(badata_gm12878_10kb))
all_rfperfs$Resolution <- rep("10 kb", length(badata_gm12878_10kb))
all_rfperfs$Resampling <- c(rep("None", 4),
                            rep("ROS", 4),
                            rep("RUS", 4),
                            rep("SMOTE", 4))
all_rfperfs$Predictor <- c("Distance", "OC", "OP", "Signal")
all_rfperfs$Chromosome <- c(rep("CHR1", 16),
                            rep("CHR2", 16),
                            rep("CHR3", 16),
                            rep("CHR4", 16),
                            rep("CHR5", 16),
                            rep("CHR6", 16),
                            rep("CHR7", 16),
                            rep("CHR8", 16),
                            rep("CHR10", 16),
                            rep("CHR11", 16),
                            rep("CHR12", 16),
                            rep("CHR13", 16),
                            rep("CHR14", 16),
                            rep("CHR15", 16),
                            rep("CHR16", 16),
                            rep("CHR17", 16),
                            rep("CHR18", 16),
                            rep("CHR19", 16),
                            rep("CHR20", 16),
                            rep("CHR21", 16),
                            rep("CHR22", 16))

@@

ggplot(d, aes(x=Predictor, y=Performance,fill=Resampling)) +
    geom_bar(position=position_dodge(), stat="identity")+
    geom_errorbar(aes(ymin=Performance-PerformanceSD, ymax=Performance+PerformanceSD), width=1,
                  position=position_dodge(0.9)) +
    #facet_grid(. ~ Predictor)+
    theme_minimal() +
    theme_bw()+
    xlab("Predictor Type") + 
    ylab("Balanced Accuracy") + #ylim(-.1,.5) +
    scale_color_discrete(name="Resampling Technique")+
    guides(shape=FALSE, linetype=FALSE)+
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    strip.text.x = element_text(size = 15),
    strip.text.y = element_text(size = 15),
    #panel.spacing = unit(2, "lines"),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20),
    legend.position="bottom")
```

@@

## ARROWHEAD WHOLE GENOME

### 2020-05-06 Scripts_for_results/09_visualizing_example_of_preciseTAD_predictions.Rmd
edits

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      CHR="CHR22",
                      CHR="CHR21",
                      #chromCoords=list(17389000,18011000),
                      chromCoords=list(15150000,17270000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), #or list(10000,3)
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=FALSE,
                      samples=100)

@@

ggplot() + 
  geom_line(data=predprobdata, aes(x=basenum, y=prob), 
            color='black',
            size=1)+
  #geom_vline(data=predicteddata, aes(xintercept=basenum, 
  #                                   color="red"),
  #           size=.5,
  #           show.legend = TRUE)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="green"),
             size=.75,
             show.legend = TRUE)+
  xlab("Base Pair Coordinate") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "green"),
                     labels = c("ARROWHEAD",
                                "preciseTAD"))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")

>>>>

pt <- preciseTAD(bounds.GR=bounds.GR,
                      genomicElements.GR=genomicElements.GR,
                      featureType="distance",
                      #CHR="CHR22",
                      CHR="CHR21",
                      #chromCoords=list(17389000,18011000),
                      chromCoords=list(15150000,17270000),
                      tadModel=tadModel[[1]],
                      threshold=1.0,
                      flank=NULL,
                      verbose=TRUE,
                      seed=123,
                      parallel=FALSE,
                      cores=NULL,
                      splits=NULL,
                      method.Dist="euclidean",
                      DBSCAN=TRUE,
                      DBSCAN_params=list(5000,3), #or list(10000,3)
                      method.Clust=NULL,
                      PTBR=TRUE,
                      CLARA=FALSE,
                      samples=100)

@@

ggplot() + 
  geom_line(data=predprobdata, aes(x=basenum, y=prob), 
            color='black',
            size=1)+
  #geom_vline(data=predicteddata, aes(xintercept=basenum, 
  #                                   color="red"),
  #           size=.5,
  #           show.legend = TRUE)+
  geom_vline(data=calleddata, aes(xintercept=basenum, 
                                  color="blue"),
             size=.75,
             show.legend = TRUE)+
  geom_vline(data=predicteddata2, aes(xintercept=basenum, 
                                      color="forestgreen"),
             size=1,
             show.legend = TRUE)+
  annotate(geom = "segment",x = 15492234, xend = 15519798,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  annotate(geom = "segment",x = 15635994, xend = 15792137,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  annotate(geom = "segment",x = 16147181, xend = 16244962,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  annotate(geom = "segment",x = 16845543, xend = 16958034,y = -Inf, yend = -Inf,color = "yellow",size = 5) +
  xlab("Base Pair Coordinate") +
  ylab("Probability") +
  scale_color_manual(name = '', 
                     values =c("blue", "forestgreen"),
                     labels = c("ARROWHEAD",
                                "preciseTAD"))+
  scale_y_continuous(breaks=c(0,.5,1), limits=c(0,1))+
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "bottom")
